
\noindent We are particularly grateful to the organized efforts of those maintaining the \textcolor{blue}{\href{http://scdb.wustl.edu/}{Supreme Court Database}}, which is principally hosted by Washington University in St.Louis, Missouri.\footnote{Harold J. Spaeth, Lee Epstein, et al. 2022 Supreme Court Database, Version 2022 Release 1. URL: \url{http://Supremecourtdatabase.org}} Their data was pivotal for constructing longitudinal analyses that place the Justices' decision-making during the 2023 term into the broader scope of history. \\

\noindent Apart from data used to develop longitudinal analyses, this report was compiled independently and drew on a multitude of resources to sufficiently track developments and behaviors expressed in the Court's oral arguments, decisions, and docket, among other things. These include, but are not limited to, the Supreme Court's \textcolor{blue}{\href{https://www.supremecourt.gov/}{Official Website}}, \textcolor{blue}{\href{https://www.oyez.org/}{Oyez}}, and \textcolor{blue}{\href{https://www.justia.com/}{Justia}}, among others. \\

\noindent All data and accompanying replication files used to compile this report are available \textcolor{blue}{\href{https://jaketruscott.github.io/}{HERE}}. For guidance on data usage and replication, please see the document entitled \emph{Data and Replication Guide}. Among these are a folder entitled \emph{Data Files}, which offers a collection of Excel (.xlsx) and R (.Rdata) files containing data relevant to the accompanying analyses on \emph{Decisions} and \emph{Oral Arguments} provided in this report. Alternatively, replication files can be found in the \emph{Replication Files} folder, which contains relevant code to reproduce all of the report's figures and tables in the R Programming Language. \\

\noindent We are, of course, happy to provide any additional insights and guidance on replication of data and other analysis in this report. For help, please \textcolor{blue}{\href{mailto:adam@feldmannet.com}{Contact Us}}. \\

\noindent These files and accompanying data are free and available for public use. We just ask that any publication incorporating these data or other material from our report provide a corresponding citation acknowledging the authors and EmpiricalSCOTUS. \\

\noindent Example Citation: Feldman, A. \& Truscott, J. S. (2024, June 30). Supreme Court 2023-2024 Term Stat Pack (Version 0.1). \emph{EmpiricalSCOTUS}. Available at: \url{https://empiricalscotus.com/}